Statistical Theory\\ Chess Dataset Analysis

### 2024-09-30 Article/Article.tex
Added statistical tests

\subsection{Connection Between Player Rating and Game Length}
To investigate whether player ratings are associated with game length, we divided players into two groups based on their ratings: those with ratings higher than 1500 (high-rated) and those with ratings lower than 1500 (low-rated). The threshold of 1500 was chosen because it represents the starting rating on the Lichess platform. The empirical cumulative distribution function (ECDF) of game lengths for both groups (Figure~\ref{fig:ecdf_plot}) shows that high-rated players generally play longer games.

\subsubsection*{Mann-Whitney U Test for Game Length}
Since we could not confirm the normality of the rating distribution, we applied the non-parametric Mann-Whitney U test to compare the game lengths between high-rated and low-rated players. Our null hypothesis was that high-rated players do not play longer games than low-rated players on average. The test returned a p-value of \(2.7 \times 10^{-73}\), which allows us to reject the null hypothesis. Therefore, we conclude that player rating significantly influences game length, with higher-rated players tending to play longer games.

>>>>

\subsection{Connection Between Player Rating and Game Length}
To investigate whether player ratings are associated with game length, we divided players into two groups based on their ratings: those with ratings higher than 1500 (high-rated) and those with ratings lower than 1500 (low-rated). The threshold of 1500 was chosen because it represents the starting rating on the Lichess platform.
\subsubsection*{Mann-Whitney U Test for Game Length}
Since we could not confirm the normality of the rating distribution, we applied the non-parametric Mann-Whitney U test to compare the game lengths between high-rated and low-rated players. Our null hypothesis was that high-rated players' game length mean wasn't higher than low-rated players' mean. The test returned a p-value of \(2.7 \times 10^{-73}\), which allows us to reject the null hypothesis. Therefore, we conclude that player rating significantly influences game length, with higher-rated players tending to play longer games.
